\documentclass[a4paper, 11pt]{article}

\input{../global-preamble.tex}

\documentsetup{Access Fund FAQs}{Helping to make Camp 100 more accessible to all}{02 September 2024}{access-fund}{en}{proof}

\begin{document}
\makedocumenttitlepage
Woodcraft Folk is keen to increase and widen participation in all of our activities. The Camp 100 Access Fund has been designed to reduce the financial barriers of attending the event including travel costs.

\section{What is the Access Fund?}
Woodcraft Folk wants to reduce the financial barriers experienced by young people and volunteers. The access fund will be used to offer reduced ticket places to individuals, including potentially free places to those who need it the most.

The Camp 100 coordination team will prioritise requests from young people and volunteers with a role at camp (at a village or central level).

Priority will be given to individuals who meet the criteria below. However we understand there are a range of reasons people struggle to afford camp and this is not an exhaustive list

\begin{itemize}
    \item Are eligible for free school meals
    \item Receive Universal Credit
    \item Would describe themselves as disabled
    \item Identify as a person of colour
    \item Attend a new Woodcraft Folk group, one registered in 2023, 2024 or 2025
    \item Attend a small Woodcraft Folk group, one with less than 7 recorded young members
    \item Those without support from district/group fundraising activities
    \item Will need to travel more than 150 miles to get to camp
\end{itemize}

\section{How do I apply?}
To apply, simply complete \href{https://forms.gle/aSqy3JNRQqcNRTE79}{this short Google Form}.

Requests should be submitted for individuals and not as a group. The form can be filled in by an individual, parent/carer or a group leader.

\section{When can I apply?}
We will be launching our first phase of the access fund in September 2024. The Camp 100 team will then decide on outcomes in December 2024 for those who have applied. To ensure everyone who needs it can benefit from the access fund we will reopen applications in January 2025 and make decisions at the end of March. We hope that this will mean everyone who needs it has a chance to access the fund and not just those who fill in the form very early. 

\section{Who should fill in the request form?}
A request form can be submitted for anyone attending the camp - a young person or a volunteer.

The form can be completed on behalf of a young person by their parent/carer or group leader. Please complete the form as if filling it in for the individual requesting financial support.

An individual request must be submitted for each individual requesting financial support.

\section{What questions will I be asked?}
The Camp 100 coordination team has made the request process as simple as possible. In the google form you will be asked why you are applying to the access fund but it is optional to answer this. 

Applicants will also be asked how much (if anything) they feel they (or their group/district) can contribute to the camp fees. This ensures that as many people as possible can benefit from the fund. 

.\section{When will I know the outcome of my application?}
For those who apply between 1 September - 30 November 2024, decisions will be communicated directly to individuals by the end of December. For the second round of applications (between Jan-March), decisions will be communicated by the end of March 2025 in plenty of time for the booking deadline in May. 
If you have already made a booking the admin team will update your ticket price on the booking system automatically. 

If you haven't already made a booking, you will be encouraged to do so by May 18th at which point the admin team will update your ticket price.

\section{How much funding can I expect to receive?}
In the application form you will be asked how much you feel you or your group/district could contribute towards camp fees (this could be £0). 

We will aim to cover the requested costs however depending on the number of applications this may not be completely possible.

\section{How will decisions be made?}
The Camp coordination team will not seek additional evidence, and will only use the information provided on the request form.

Each request will be reviewed by coordinators and staff and we aim to spread the access fund as equitably and fairly as possible based on the requests in the completed form. 

\section{What can I do if I am unsuccessful or require additional support to attend the event?}
What can I do if I am unsuccessful or require additional support to attend the event?
Reapply if unsuccessful in first round - once we know what we have might have more in the second round to share with others 

Many districts fundraise to help bring their group to camp and we would recommend trying this too if you can. Local groups are encouraged to seek funding from local organisations, such as Rotary Clubs, Lions groups etc. See our fundraising page on the Camp 100 website for more info on grants and other ways your group can raise funds.

Alternatively, groups should consider collectively engaging in fundraising activities, such as cake sales and pea fayres.

For support with fundraising activities please contact fundraising@woodcraft.org.uk 

\section{Who can I contact for more information?}
Please contact email info@camp100.org.uk 


\makedocumentbackpage

\end{document}