\documentclass[a4paper, 11pt]{report}

\input{../global-preamble.tex}

\documentsetup{How to pay for Camp 100}{How to give Camp 100 all your money}{24 August 2024}{how-to-pay}{en}{v2}

\begin{document}
\makedocumenttitlepage

\tableofcontents

\chapter{UK Payments}

\begin{callout-green}{Information}
We strongly encourage that groups pay camp fees by bank transfer where possible.
\end{callout-green}

Please transfer all payments into the following account\\
\textbf{Account name:} Woodcraft Folk\\
\textbf{Account number:} 2039 2756\\
\textbf{Sort code:} 60 83 01

Check the unique reference on your Booking confirmation, ie. \verb|C100-XXXXX| Please ensure you will use this reference for the deposit and all subsequent payments.

If for any reason you cannot add a reference, please send an email to info@camp100.org.uk and let us know how much you paid, when you paid it and who it was for. We can then match it to your booking and bring your payment record up to date.

Individuals who are booking into Camp 100 can pay by card (We ask that any payment for over 3 people is \textbf{not} made by card). When booking as an individual you will be sent a link to pay on card via Stripe.

\textbf{If you cannot complete the payment via BACS you can send a cheque:}

Please make all cheques payable to `Woodcraft Folk'.

If you are paying by cheque please email info@camp100.org.uk to let us know you have sent the cheque and who it is paying for. 

Post your cheque to:\\
Woodcraft Folk\\
Holyoake House\\
Hanover Street\\
Manchester \\
M60 0AS\\

\chapter[International Payments]{International\\ Payments}

\begin{callout-green}{Information}
We strongly encourage that international groups pay camp fees by bank transfer where possible. 
\end{callout-green}

Please transfer all payments into the following account:\\
\textbf{Swift Code (BIC):} NWBKGB2L\\
\textbf{IBAN Number:} GB93NWBK60023571418024\\
\textbf{Address of organisation:} \\
Holyoake House, Hanover Street, Manchester, M60 0AS, United Kingdom

Check the unique reference on your Booking confirmation, ie. \verb|C100-XXXXX|. Please ensure you will use this reference for the deposit and all subsequent payments. 

If for any reason you cannot add a reference, please send an email to info@camp100.org.uk and let us know how much you paid, when you paid it and who it was for. We can then match it to your booking and bring your payment record up to date

\makedocumentbackpage

\end{document}