\documentclass[a4paper, 11pt]{report}

\input{../global-preamble.tex}

\documentsetup{Payment Policy}{Payments, Deposits, Refunds, and more}{01 July 2024}{payment-policy}{en}{v1}

\begin{document}
\makedocumenttitlepage

\tableofcontents

\chapter{For Groups}
\begin{callout-green}{Information}
Please contact us on info@camp100.org.uk if you need this information presented in a different way, or anything is unclear. The camp booking is a financial commitment and we want you to feel happy and comfortable about your decision. 
\end{callout-green}

\section{Camp fees}
\begin{table}[H]
    \centering
    {\RaggedRight
    \begin{tabular}{p {0.17\textwidth} p{0.32\textwidth} p{0.11\textwidth} p{0.11\textwidth} p{0.11\textwidth}}
    \tablehead{Region} & \tablehead{Countries} & \tablehead{10 day\newline (27 July - 6 August)} & \tablehead{3 days\newline (27 - 30 July)} & \tablehead{7 days\newline (30 July - 6 August)}\\
    Western and Northern Europe, North America & Austria, Belgium, Catalonia, Denmark, Finland, Germany, Italy, Norway, Switzerland, UK, Canada & £265 & £120 & £210 \\
    \hline
    Eastern Europe and some Middle East & Armenia, Belarus, Czech Republic, Georgia, Hungary, Lithuania, Slovakia, Slovenia, Turkey, Israel & £190 & 85 & 150\\
    \hline
    Africa, Asia, Latin America and some Middle East & Cameroon, Egypt, Ghana, Malawi, Mali, Senegal, Western Sahara, Zimbabwe, Bhutan, India, Indonesia, Nepal, Bolivia, Chile, Nicaragua, Paraguay, Peru, Palestine & £130 & £55 & 100\\
    \hline
    \end{tabular}
    } % end of rr     
    \caption{Camp Fees breakdown by region and attendance length for members of a group booking}
    \label{tab:group-camp-fees}
\end{table}

Participants aged 0 - 5 do not pay a camp fee. However all under 5's do need to be booked on, for safety and planning reasons.

See booking deadline below.

The camp fee includes food, all the activities on site and the central infrastructure. Travel to camp is not included but a shuttle bus from a nearby station on the first and last days will be. 

\section{Deposits}
Your group booking is secure after you have paid 50\% of your delegation costs. The deposit is non-refundable but will be taken out of your group's remaining balance.

\section{Paying the remaining balance}
You need to have paid the remaining balance for your group by 10 June 2025 but please make payments as soon as your group can afford to: The funds raised will go towards making the camp sound, look, taste and smell even better! 

We will not be allowing any group access to camp if their fees have not been paid in full upfront. This is in fairness to all the other delegations who have paid by the deadline.

\section{Payment Deadline}
The final booking deadline for Camp 100 will be \textbf{10 June 2025, we ask that all groups have paid in full for all participants by this date}. After this date food orders will be placed and infrastructure will be secured and we would not be able to guarantee that dietary and accessibility needs would be met if we were to take late booking. Applications to book after the deadline are extremely unlikely to be accepted. Please ensure to book and pay by the deadline in order to avoid disappointment. 

You will also need to ensure that DBS checks or safeguarding agreements (for international groups) are in place before camp for all participants aged 16 or over. We will not be allowing access to camp for anyone without valid and appropriate safeguarding clearance. 

We reserve the right to increase the camp fee for any booking made after the deadline.

\section{Cooling-off period}
There is a cooling-off period of 14 days from the time when you first pay the deposit to change your mind. In this time period, you are eligible for a full refund and your group does not have to give a reason for the cancellation. 

\section{Refunds}
The camp fees generally go towards upfront costs.  For this reason, we regret to say we are unable to offer refunds to groups who withdraw prior to attending. 

In the unlikely event that you book onto camp and your group is then unable to take part, please first try to find replacement participants and group leaders. This is to avoid disappointing any young people who have already been expecting to attend. Then contact info@camp100.org.uk where our team will make every effort to support you in finding a satisfactory solution. There is guidance available for fundraising, an access fund to support campers for whom finances are a barrier and support for accessing camping equipment. You are important to us and we want to enable as many groups as possible to attend.
 
If during camp you are unsatisfied with the experience, please contact camp management on site, at the earliest opportunity. We want everyone to enjoy their experience and will actively work with you to resolve the issue. We regret to say that at the time of the camp, the expense has already been incurred and we are unable to offer refunds. Please use the camp procedures or Woodcraft Folk complaints policy for raising issues.


\chapter[For Individual Participants]{For Individual\\Participants}
\begin{callout-green}{Information}
Please contact us on info@camp100.org.uk if you need this information presented in a different way, or anything is unclear. The camp booking is a financial commitment and we want you to feel happy and comfortable about your decision. 
\end{callout-green}

Participation at camp is encouraged as part of a group. This is for your social, safety and financial benefit. Participants are likely to have a much richer experience attending with a group. However UK participants over the age of 16 can choose to book independently if there is no alternative. We are unable to support applications for individual participants from outside the UK unless they are delivering programme or taking on a central role.

\begin{table}[H]
    \centering
    {\RaggedRight
    \begin{tabular}{p{0.45\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
    \tablehead{Region} & \tablehead{10 day (27 July - 6 August)} & \tablehead{3 days (27 - 30 July)} & \tablehead{7 days (30 July - 6 August)}\\
    UK Participants aged over 16 & £265 & £120 & £210 \\
    \hline
    \end{tabular}
    } % end of rr     
    \caption{Camp Fees breakdown by region and attendance length for individual participants}
    \label{tab:individual-camp-fees}
\end{table}

You will also need to be a paid-up member of Woodcraft Folk with suitable DBS/PVG or safeguarding checks in place before attending the event. 

\section{Deposits}
Your booking is secure after you have paid the equivalent of 50\% of your booking (e.g. for 10 days £132.50). 

The deposit is non-refundable but will be taken out of your remaining balance.

If you have difficulties paying, please contact info@camp100.org.uk and we will make every effort to give options to pay via card, BACS, over the phone or in smaller instalments. 

\section{Paying the remaining balance}
You need to have paid the remaining balance by 10 June 2025.

We will not be allowing any participant access to camp if their fees have not been paid in full upfront. This is in fairness to all the groups and individuals who have paid by the deadline.

However please do contact us directly at info@camp100.org.uk if you are in a financially difficult situation and need help with fundraising ideas or other support. We will not put you under pressure to attend if you have changed your mind.

\section{Payment Deadline}
The final booking deadline for Camp 100 will be \textbf{10 June 2025, we ask that all campers have paid in full for all participants by this date.} After this date food orders will be placed and infrastructure will be secured and we would not be able to guarantee that dietary and accessibility needs would be met if we were to take late booking. Applications to book after the deadline are extremely unlikely to be accepted. Please ensure to book and pay by the deadline in order to avoid disappointment. 

You will also need to ensure that you have completed DBS checks or a safeguarding agreement (for international groups) before camp. We will not be allowing access to camp for anyone without valid and appropriate safeguarding clearance. 

We reserve the right to increase the camp fee for any booking made after the deadline.

\section{Cooling-off Period}
There is a cooling-off period of 14 days from the time when you first pay the deposit to change your mind. In this time period, you are eligible for a full refund and you do not have to give us a reason for your cancellation. 

\section{Refunds}
The camp fees generally go towards the camp infrastructure, food and other upfront costs.  For this reason, we regret to say we are unable to offer refunds to anyone who withdraws. However we understand that losing a sum of money could put you in hardship. \textbf{Therefore please speak to us at the earliest opportunity if you have payment difficulties. We want to help you with fundraising advice and with practicalities.} Please contact us on info@camp100.org.uk. You will not be pressured into attending the camp if you don't want to.
 
If during camp you have any problems, please contact camp management on site, at the earliest opportunity. We want everyone to enjoy their experience and will actively work with you to resolve the issue. We regret to say that at the time of the camp, the expense has already been incurred and we are unable to offer refunds. Please use the camp procedures or Woodcraft Folk complaints policy for raising issues.


\makedocumentbackpage

\end{document}